I don't know, are you sure we want to do this?\\ Sea level adaptation decisions under uncertainty

### 2016-12-14 submission/paper.tex
Updates to Bergen example in paper

\section{Sea level projections {\color{blue} (PG)}}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\linewidth]{DamageDistribution.pdf}
\caption{ The estimated distribution of annual storm surge damage in Bergen for 2015 (red) based on observed annual damage in Hordaland and Rogaland 1980-2015 (gray bars). }
\label{fig:BergenDamageDist}
\end{center}
\end{figure}

@@

\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=0.5\linewidth]{EuropeanIncreaseLossExtrapolationUncertainty.pdf}
\caption{ Relative change in mean annual damage as a function of sea level rise for 15 European cites as estimated by \cite{Hallegatte&2013} (black circles) with linearly extrapolated values indicated by gray lines. The median change and the corresponding extrapolation are indicated in red.}
\label{fig:ChangeInDamage}
\end{center}
\end{figure}

\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=0.5\linewidth]{AccumulatedFutureLoss.png}
\caption{Distribution of log  accumulated future loss 2016-2100 under RCP 8.5 and assuming that no adaptation measures are implemented.} 
\label{fig:NoAction}
\end{center}
\end{figure}

>>>>

\section{Sea level projections}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\linewidth]{DecisionAnalysisBergen.pdf}
\caption{Damage data used in the decision analysis for Bergen: (a) Estimated distribution of annual storm surge damage in Bergen for 2015 (red) based on observed annual damage in Hordaland and Rogaland 1980-2015 (gray bars); (b) Relative change in mean annual damage as a function of sea level rise for 15 European cites as estimated by \cite{Hallegatte&2013} (black circles) with linearly extrapolated values indicated by gray lines. The median change and the corresponding extrapolation are indicated in red.}
\label{fig:BergenDamageDist}
\end{center}
\end{figure}

@@

\begin{figure}[!hbpt]
\begin{center}
\includegraphics[width=0.5\linewidth]{CumDamageCostsBergen.pdf}
\caption{Distribution of accumulated future loss 2016-2100 under RCP 8.5 and assuming that no adaptation measures are implemented.} 
\label{fig:NoAction}
\end{center}
\end{figure}
